\cvsection{Projects}

\begin{cventries}
  \cvproject
    {sFTP Client Application} % Project
    {Jan. 2019 - Mar. 2019} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Utilized Agile methodology, Git, and Python 3 in a team of 6 to develop a command line interface SFTP client.}
      \end{cvitems}
    }

 \cvproject
    {Xv6 Operation System} % Project
    {Jan. 2019 - Mar. 2019} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Improved OS scheduling by converting from Round Robin to Multi-level Feedback Queue scheduling.}
        \item {Improved process management of the OS scheduler by separating the processes by its process state.}
        \item {Implemented additional system calls and console control sequences.}
      \end{cvitems}
    }

  \cvproject
     {Convex Hull}
     {Sept. 2018 - Dec. 2018}
     {
       \begin{cvitems}
         \item {Successfully proved Quick-hull is more time efficient than Brute Force through interpreting and analyzing data sets.}
         \item {Utilized JavaScript, Jest testing framework, and Atom IDE for development.}
       \end{cvitems}
     }

  \cvproject
  {Chocoholics Data Processing Software}
  {Sept. 2018 - Dec. 2018}
  {
    \begin{cvitems}
      \item {Generated requirement documentation, reports, test plans in a team of 5 to development software that meets client's demands.}
      \item {Utilized source control (git), unit testing (Google Test Framework), and C++ to develop the software.}
    \end{cvitems}
  }

  \cvproject
    {Academic Course Plan}
    {Sept. 2017 - Dec. 2017}
    {
       \begin{cvitems}
         \item {Created a program in C++ using Depth-First Search and Topological Sorting algorithms that allows students to develop an academic course plan.}
         \item {The program utilized a graph data structure through using arrays of LLLs.}
      \end{cvitems}
    }

\end{cventries}
